A practical look at genetic algorithms

### 2015-11-22 evolutionaryComputation/practicals/report.tex
only create children if there are new genes at play

\subsubsection{Evaluate each member on creation}
\section{Execution}
%TODO:
% 1. Experiments
% Use stoastic within the algoritm
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
% maybe some more testing of the crossovers?
% also try to implement a threading scheme??

>>>>

\subsubsection{Evaluate each member on creation}
Members are going to be evaluated always, initially I would evaluate the member
everytime it needed to be evaluated, but in later version I just aded the
evaluation to the case class. Its not going to change anyways.

\subsubsection{Only create children if the genes are new}
If the genes are new then create the children otherwise return the parent.
\section{Execution}
%TODO:
% 1. Experiments
% Use stoastic within the algoritm
%	Draw a graph from the experiments
%		* pop size on x, # succes on Y
% maybe some more testing of the crossovers?
% also try to implement a threading scheme??
